### 2013-05-17 inst/examples/policycosts/writeup.Rmd
writeup run using NPV apples-to-apples #35

@@

Clean the workspace and load the required libraries.

``` {r libraries}
rm(list=ls())
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
```

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(dev.args=list(bg="transparent"),
               tidy=FALSE, comment=NA, message=FALSE)
theme_notebook <- theme_grey() + 
                  theme(plot.background = 
                          element_rect(fill = "transparent",colour = NA),
                        panel.grid.minor = 
                          element_line(colour = "transparent"))
theme_set(theme_notebook)
```

@@

``` {r  parallel}
require(snowfall)
sfInit(cpu=2, parallel=T)
sfLibrary(pdgControl)
sfExportAll()
````

@@

Note that `optim_policy` has been updated to return the equilibrium value of profits from fish harvests before the adjustment costs have been paid, `penalty_free_V`.  This contains the values for all possible states, we simply evaluate it at the carrying capacity (which is our initial condition.)  The index in `x_grid` that corresponds to the carrying capacity (initial condition) `i` indicates this.

@@

```{r}
i <- which(x_grid > K)[1]
fees <- 
lapply(policies, function(penalty) 
  sapply(penalty, function(c2_run)
    max(c2_run$penalty_free_V[i,]) 
  )
)
```

>>>>

``` {r libraries, message=FALSE, warning=FALSE}
rm(list=ls())
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
```

@@

```{r graphing-options, include=FALSE}
#opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(dev.args=list(bg="transparent"),
               tidy=FALSE, comment=NA, message=FALSE, warning=FALSE)
theme_notebook <- theme_grey() + 
                  theme(plot.background = 
                          element_rect(fill = "transparent",colour = NA),
                        panel.grid.minor = 
                          element_line(colour = "transparent"))
theme_set(theme_notebook)
```

@@

``` {r  parallel}
require(snowfall)
sfInit(cpu=16, parallel=T)
sfLibrary(pdgControl)
sfExportAll()
````

@@

Note that `optim_policy` has been updated to return the equilibrium value
of profits from fish harvests before the adjustment costs have been paid,
`penalty_free_V`, as well as the total value `V`. Initially we based the 
comparison on matching `penalty_free_V`, now the economists recommend we
simply use the total net present value resulting, `V`.

The value matrices returned in either case contain the values for all possible states,
we simply evaluate it at the carrying capacity (which is our initial
condition.)  The index in `x_grid` that corresponds to the carrying
capacity (initial condition) `i` indicates this.

@@

```{r}
i <- which(x_grid > K)[1]
fees <- 
lapply(policies, function(penalty) 
  sapply(penalty, function(c2_run)
    max(c2_run$V[i,]) # Would be penalty_free_V originally 
  )
)
```
